Back to ``Normal'' for the Disintegrating Planet Candidate KIC 12557548 b

### 2018-04-18 ms.tex
added updated histograms and periodogram.

\begin{figure*}[!hbtp]
\begin{centering}
\includegraphics[width=0.49\textwidth]{images/kepler/pca_k1255.pdf}
\includegraphics[width=0.45\textwidth]{images/kepler/amplitude_series.pdf}
\caption{Principal component eigenvectors (Left) and amplitude time series (Right).}\label{fig:secEclipse}
\end{centering}
\end{figure*}

\begin{figure*}[!hbtp]
\begin{centering}
\includegraphics[width=0.49\textwidth]{images/kepler/amplitude_histogram.pdf}
\caption{Histogram of transit amplitudes.
An amplitude of 1.0 corresponds to the average light curve (with flux minimum of 99.53\% or 0.47\% transit depth).
A comparison histogram is shown from the Kepler Secondary eclipses to show the photon noise.}\label{fig:secEclipse}
\end{centering}
\end{figure*}

>>>>

\begin{figure*}[!hbtp]
\begin{centering}
\includegraphics[width=0.49\textwidth]{images/kepler/pca_k1255.pdf}
\includegraphics[width=0.45\textwidth]{images/kepler/amplitude_series.pdf}
\caption{Principal component eigenvectors (Left) and amplitude time series (Right).}\label{fig:PCAamp}
\end{centering}
\end{figure*}

\begin{figure*}[!hbtp]
\begin{centering}
\includegraphics[width=0.49\textwidth]{images/kepler/amplitude_periodogram.pdf}
\caption{Periodogram of the amplitude time series shown in Figure \ref{fig:PCAamp}
Bootstrap error estimates for the 2$\sigma$ and 3$\sigma$ confidence intervals are shown.
The peak at 0.65 days is the orbital period.
The peaks at 153 and 750 days are likely caused by the longer intervals of low disintegration activity.}\label{fig:periodogram}
\end{centering}
\end{figure*}

\begin{figure*}[!hbtp]
\begin{centering}
\includegraphics[width=0.49\textwidth]{images/kepler/amplitude_histogram.pdf}
\includegraphics[width=0.49\textwidth]{images/kepler/deconvolved_hist.pdf}
\caption{(Lef) Histogram of transit amplitudes.
An amplitude of 1.0 corresponds to the average light curve (with flux minimum of 99.53\% or 0.47\% transit depth).
A comparison histogram is shown from the Kepler Secondary eclipses to show the photon noise.
(Right) The primary transit histogram is de-convolved by the secondary eclipse histogram to attempt to measure the intrinsic astrophysical variability.}\label{fig:histoGrams}
\end{centering}
\end{figure*}
